The imprint of global magma oceans on exoplanet demographics

### 2022-08-26 src/tex/ms.tex
add example plot of a key posterior for different surveys
add software cites

\subsection{Mission design trades}\label{sec:mission-design-trades}
\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}
\citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.

@@

>>>>

\subsection{Mission design trades}\label{sec:mission-design-trades}
\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}

\begin{note}
    \citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.
\end{note}

        \includegraphics[width=\linewidth]{figures/example_posterior_surveys.pdf}
        \caption{
        Retrieved posterior distribution of the $<key parameter>$ for different survey realizations.
        The orange line corresponds to the true value of the injected signal.
        }
        \label{fig:posterior_surveys}
    \end{centering}
\end{figure}

@@

\begin{large}\textit{Author contributions:}\end{large}

\software{
Bioverse~\citep{Bixel2021},
Astropy~\citep[][]{AstropyCollaboration2018},
NumPy~\citep[][]{Harris2020},
SciPy~\citep[][]{Virtanen2020},
corner.py~\citep{Foreman-Mackey2016b}.
}
